Exception Handling Bug Hazards in Android: Results from a Mining Study and an Exploratory Survey

### 2016-07-21 SPRINGER_JOURNAL/techreport/TUD-SERG-2016-018.tex
Add DOI
http://dx.doi.org/10.1007/s10664-016-9443-7

\note{This paper has been accepted for publication in \emph{Empirical Software Engineering}, 2016.\\
It is a substantially revised and extended version of 
Roberta Coelho, Lucas Almeida, Georgios Gousios, Arie van Deursen:
Unveiling Exception Handling Bug Hazards in Android Based on GitHub and Google Code Issues.
\emph{Working Conference on Mining Software Repositories} (MSR) 2015: 134-145.
}

>>>>

\note{This paper has been accepted for publication in \emph{Empirical Software Engineering}, 2016, where it will have DOI \url{http://dx.doi.org/10.1007/s10664-016-9443-7}.
\\[1em]
This paper is a substantially revised and extended version of 
Roberta Coelho, Lucas Almeida, Georgios Gousios, Arie van Deursen:
Unveiling Exception Handling Bug Hazards in Android Based on GitHub and Google Code Issues.
\emph{Working Conference on Mining Software Repositories} (MSR) 2015: 134-145.
}
